### 2016-08-31 version0.0/appendixa_3.tex
Changing plots in ch4. to flux density instead of flux

In Chapter~\ref{ch: paper1}, we mentioned that we used hierarchical Bayesian linear regression to fit the star formation laws (both the Kennicutt-Schmidt and the extended Schmidt law).
The goal is to find the star formation laws using observational data.
In order to compare our results with previous studies and testing star formation laws, we chose to use linear regression to fit the data.
Hierarchical Bayesian regression fitting method were chosen over the simple linear regions methods (e.g. ordinary least square fitting) due to fact that this method thoroughly accounts for all the measured uncertainties and considers the hierarchical data structure (if there is any).
\cite{Shetty13} described the fitting using hierarchical Bayesian linear regression in detail.
In this section, we first summarize \cite{Shetty13} approach and then we describe how we extended their code to fit multiple hierarchical Bayesian regression in order to investigate the extended Schmidt law.

>>>>

In Chapter~\ref{ch: paper1}, we mentioned that we used hierarchical Bayesian linear regression to fit the star formation laws (both the Kennicutt-Schmidt and the extended Schmidt law).
The goal is to find the star formation laws using observational data.
In order to compare our results with previous studies and testing star formation laws, we chose to use linear regression to fit the data.
Hierarchical Bayesian regression fitting method were chosen over the simple linear regions methods (e.g. ordinary least square fitting) due to fact that this method thoroughly accounts for all the measured uncertainties and considers the hierarchical data structure (if there is any).
\cite{Shetty13} described the fitting using hierarchical Bayesian linear regression in detail.
In this section, we first summarize \cite{Shetty13} approach and show the differences between ordinary least square fitting and the hierarchical Bayesian linear regression and then we describe how we extended their code to fit multiple hierarchical Bayesian regression in order to investigate the extended Schmidt law.
